\documentclass[11pt]{article}

\usepackage{amsmath, amssymb}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{geometry}
\usepackage{hyperref}

\geometry{margin=1in}

\title{Macro Event Risk and Cross-Asset Correlation Breakdown}
\author{Your Name}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
Macroeconomic announcements are a primary driver of short-horizon risk in global markets.
This paper studies how major macro events such as CPI, Non-Farm Payrolls, and FOMC decisions
impact equities, foreign exchange, rates, and volatility at intraday horizons.
We further show that macro events are associated with statistically significant shifts
in cross-asset correlation structure, indicating temporary breakdowns in diversification.
\end{abstract}

\section{Introduction}
Macro announcements introduce concentrated information shocks.
Unlike continuous trading risk, event risk manifests as abrupt repricing across asset classes.
Understanding both directional reactions and correlation dynamics around events
is critical for portfolio construction and risk management.

\section{Data}
We use intraday market data at five-minute frequency for equities, FX, rates, and volatility.
Macro event timestamps are obtained from an economic calendar API and aligned precisely
with market data to capture immediate post-release reactions.

\section{Methodology}

\subsection{Event Alignment}
For each macro event at time $t_0$, we extract a symmetric window
$[t_0 - \Delta, t_0 + \Delta]$ and normalize prices relative to pre-event levels.

\subsection{Event Impact Metrics}
We compute:
\begin{itemize}
\item Event return
\item Event volatility
\item Cross-asset reaction dispersion
\end{itemize}

\subsection{Correlation Breakdown Analysis}
Rolling correlation matrices are computed before and after each event.
We measure correlation shifts using:
\[
\Delta \bar{\rho} = \bar{\rho}_{post} - \bar{\rho}_{pre}
\]
where $\bar{\rho}$ is the average pairwise correlation.

\section{Empirical Results}

\subsection{Single-Event Reactions}
Figure~\ref{fig:event} shows the S\&P 500 reaction to a CPI release,
highlighting abrupt repricing immediately following the announcement.

\subsection{Cross-Asset Response}
Figure~\ref{fig:crossasset} illustrates divergent responses across equities,
FX, rates, and volatility, reflecting heterogeneous macro transmission channels.

\subsection{Correlation Shifts Around Events}
We observe systematic increases in average cross-asset correlation following
high-impact events, indicating temporary diversification breakdowns.

\section{Discussion}
Macro events act as coordination points for market participants,
compressing correlation structure and amplifying systemic risk.
These effects are strongest during already fragile macro regimes.

\section{Conclusion}
Event-driven correlation dynamics highlight the importance of
macro-aware risk management. Static diversification assumptions
fail during periods of concentrated information release.

\bibliographystyle{plain}
\bibliography{references}

\end{document}
